---
output:
  html_document:
    keep_md: yes
---
## gameday

`gameday` package provides  an easy way to check whether your favorite NHL team has a game today (or any other days) or not, and also can offer you the score information for all the games on a certain day.

### Installation

The packages can be installed from `github`.
```{r eval= FALSE}
# install from github
library("devtools")
install_github("JiyingWen/gameday")
```

### Usage
There are two main functions in current version: `gday(team, date)` and `scores(date)`.

For example, we want to know whether Montreal Canadiens has a game on "2014-11-25", we can call `gday(team, date)`:
```{r}
# load package
library(gameday)

gday("canadiens", "2014-11-25")
```

We also want to know the scores of all the games played on "2014-11-20", we can call `scores(date)`:
```{r}
scores("2014-11-20")
```

### Vignette
A more detailed description of `gameday` package can be found in the vignette. To view it, run the following `R` code in the console.
```{r eval = FALSE}
browseVignettes("gameday")
```

