---
title: "Gameday"
author: "Jiying Wen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

## Introduction

The package has two main functions: `gday(team, date)` and `scores(date)`. `gday()` provides an easy way to check whether your favorite NHL team has a game today (or any other days) or not, `scores()` can offer you the score information for all the games on a certain day.

The package can be installed using `devtools` from `github` repository.

```{r}
#devtools::install_github("JiyingWen/gameday")
```

## Usage

We need to load the package first.

```{r}
library(gameday)
```

### gday()

The default of `gday()` is to check if Vancouver Canucks has a game on `Sys.Date`(today).

```{r}
# check whether Canucks has a game today
gday()
```

We can also check any other teams we are interested in.

```{r}
# check whether New York Rangers plays tomorrow
gday("rangers", Sys.Date() + 1)
```

We can specify the date using format "YYYY-MM-DD"
```{r}
# check whether Boston Bruins plays on Nov. 25, 2014
gday("Bruins", "2014-11-25")
```

### scores()
The default of `scores()` is to return a `data.frame` with information of games on `Sys.Date` (today).
```{r}
# check the scores today
scores()
```
Of course we can specify the date using `YYYY-MM-DD` format.
```{r}
# check the scores on Nov.18, 2014
scores("2014-11-18")
```
In the `game_status`, 1 = scheduled, 3 = in progress, 5 = finished.

We can filter out the games that have ended and get the number of total shots in each game.
```{r}
# load dplyr package
suppressPackageStartupMessages(library(dplyr))
#filter out the games that have ended and calculate total shots
shots <- scores() %>%
	filter(game_status == 5) %>%
	mutate(total_shots = home_shots + away_shots) %>%
	select(home, away, home_score, away_score, total_shots)
```

```{r results='asis'}
library(knitr)
kable(shots, format = "html")
```

We can also find the winning teams for the day.

```{r}
(
	winning_teams <- scores() %>%
    mutate(winning_team = ifelse(home_score > away_score, 
    														 as.character(home), as.character(away))) %>%
    select(winning_team)
	)

```


